Submission 2.1

### 2023-09-19 Submission 2.1.tex
Fix question 9
Day 13 HW

\begin{flushleft}
    For problems 2-15: \textit{Write a sentence in quantificational logic that captures as much of the given information as possible. Remember to delineate the extensions you assign to names and predicates.}
\end{flushleft}
\begin{enumerate}
    \setcounter{enumi}{1}
    \item All's well that ends well. (Shakespeare) (B 148)\\
          Ax: x is well\\
          Bx: x ends well\\
          $\forall x(Bx \to Ax)$
    \item The things which are seen are temporal; but the things which are not seen are eternal. (II Corinthians 4:18) (B 169)\\
          Ax: x is seen\\
          Bx: x is eternal\\
          $\forall x((Ax \to \neg Bx) \land (\neg Ax \to Bx))$, which is equivalent to $\forall x (Ax \leftrightarrow \neg Bx)$.
    \item \includegraphics{2.1.4} \\
          Ax: x is in A\\
          Bx: x is in B\\
          $\forall x(Ax \to Bx)$
    \item \includegraphics{2.1.5}\\
          Ax: x is in A\\
          Bx: x is in B\\
          $\forall x(Ax \leftrightarrow \neg Bx)$
    \item If you don't love yourself, you can't love anybody else.\\
          Lxy: x loves y\\
          y: you\\
          $\neg Lyy \to \neg \exists x(Lyx)$
    \item NSYNC is the best band ever.\\
          n: NSYNC\\
          A: is the best band\\
          $An$
    \item Somebody loves everybody.\\
          Axy: x loves y\\
          $\exists x \forall y (Axy)$
    \item There is someone for everybody.\\
          Axy: There is x for y\\
          $\exists x \forall y(Axy)$
    \item Scrooge doesn't love anybody.\\
          Axy: x loves y\\
          s: Scrooge\\
          $\neg \exists x (Lsx)$
    \item Only the shallow know themselves. (Oscar Wilde) (B 169)\\
          Ax: x is shallow\\
          Bx: x knows itself\\
          $\forall x(Bx \to Ax)$
    \item Everybody has a mother.\\
          Ax: x has a mother\\
          $\forall x(Ax)$
\end{enumerate}

>>>>

\begin{flushleft}
      For problems 2-15: \textit{Write a sentence in quantificational logic that captures as much of the given information as possible. Remember to delineate the extensions you assign to names and predicates.}
\end{flushleft}
\begin{enumerate}
      \setcounter{enumi}{1}
      \item All's well that ends well. (Shakespeare) (B 148)\\
            Ax: x is well\\
            Bx: x ends well\\
            $\forall x(Bx \to Ax)$
      \item The things which are seen are temporal; but the things which are not seen are eternal. (II Corinthians 4:18) (B 169)\\
            Ax: x is seen\\
            Bx: x is eternal\\
            $\forall x((Ax \to \neg Bx) \land (\neg Ax \to Bx))$, which is equivalent to $\forall x (Ax \leftrightarrow \neg Bx)$.
      \item \includegraphics{2.1.4} \\
            Ax: x is in A\\
            Bx: x is in B\\
            $\forall x(Ax \to Bx)$
      \item \includegraphics{2.1.5}\\
            Ax: x is in A\\
            Bx: x is in B\\
            $\forall x(Ax \leftrightarrow \neg Bx)$
      \item If you don't love yourself, you can't love anybody else.\\
            Lxy: x loves y\\
            y: you\\
            $\neg Lyy \to \neg \exists x(Lyx)$
      \item NSYNC is the best band ever.\\
            n: NSYNC\\
            A: is the best band\\
            $An$
      \item Somebody loves everybody.\\
            Axy: x loves y\\
            $\exists x \forall y (Axy)$
      \item There is someone for everybody.\\
            Axy: There is x for y\\
            $\forall y \exists x(Axy)$\\
            \textit{Note: the order of quantifiers matters!}
      \item Scrooge doesn't love anybody.\\
            Axy: x loves y\\
            s: Scrooge\\
            $\neg \exists x (Lsx)$
      \item Only the shallow know themselves. (Oscar Wilde) (B 169)\\
            Ax: x is shallow\\
            Bx: x knows itself\\
            $\forall x(Bx \to Ax)$
      \item Everybody has a mother.\\
            Ax: x has a mother\\
            $\forall x(Ax)$
      \item There are at least two pigs.\\
            Px: x is a pig\\
            $\exists x \exists y (Px \land Py \land (x \neq y))$
      \item There are exactly two pigs.\\
            $\exists x \exists y \exists z (Px \land Py \land x \neq y \land ((z \neq x \land z \neq y) \to \neg Pz))$
      \item There are at most two pigs.\\ 
            $\neg \exists x \exists y \exists z (Px \land Py \land Pz \land (x \neq y \land x \neq z \land y \neq z))$
            \textit{(there are not 3 unique pigs)}

\end{enumerate}
